---
title: "Are You Your Work Analysis"
author: "Steve Leathers"
date: "Monday, June 29, 2015"
output: html_document
---

Grab the data with read.csv, using the pipe character as a separator.

```{r}
ayyw = read.csv("ayyw.csv", sep="|")
```

Add the ggplot2 and tm libraries.

```{r}
library(ggplot2)
library(tm)
```

How did people answer the question "Are you your work?"

```{r, echo=FALSE}
qplot(answer, data=ayyw)
```

Create a dataframe to anaylze text, toss it all in one big chunk.
```{r}
ans = paste(ayyw$explanation, collapse = " ")
```

Create a vector source of all of the responses.
```{r}
vs = VectorSource(ans)
```

Turn that vector source into a corpus.
```{r}
corpus = Corpus(vs)
```

Make all text lower case, remove all punctuation, whitespace and stop words ("I", "me", "my", etc).
```{r}
corpus <- tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords("english"))
```

Turn the corpus into a Document Term Matrix
```{r}
dtm = DocumentTermMatrix(corpus)
dtm2 = as.matrix(dtm)
```

Turn the frequency counts into a sorted dataframe.
```{r}
frequency = colSums(dtm2)
frequency = sort(frequency,decreasing=TRUE)
words = names(frequency)
words


head(frequency)
```

